### 2019-08-30 Writeup/Thesis/chapters/abstract.tex
Changes; - TTS run over the entire paper and corrections added

This work implements an attack on Trustwords and quantifies its effectiveness on more than 400 participants.  A tool called GreenOnion was designed to assist in quantifying attack feasibility. GreenOnion improved substantially on a similar tool's ability to search for matches concurrently. Our findings show a substantial increase in attack success compared to related literature. We believe this increase is due to leveraging the design flaws in the Trustword scheme.

>>>>

This works main aim is to asses if Trustword's recommend minimum number of four words is sufficient.
In order to achieve this goal, this work implements an attack on Trustwords and quantifies its effectiveness on more than 400 participants.  A tool called GreenOnion was designed to assist in quantifying attack feasibility. GreenOnion improved substantially on a similar tool's ability to search for matches concurrently where it was able to search for over 1.5 million concurrent keys. Our findings show a substantial increase in attack success compared to related literature. We believe this increase is due to levering the design flaws in the Trustword scheme. Therefore, we believe a minimum of four Trustwords is insufficient to provide even a basic level of security.

### 2019-08-30 Writeup/Thesis/chapters/design.tex
Changes; - TTS run over the entire paper and corrections added

These attacks are ascending in complexity. The timeframe for computing a near-collision was decided as 7-days with attack strengths of 1 GPU-day, 10 GPU-days and 100 GPU-days on a mid-range GPU (AMD RX 480). Due to the long lifetime of PGP keys, 7 days was chosen as a reasonable length of the attack. The tool requires no user interaction once started, therefore, it can be left for an extended period to compute potential keys. This timeframe is also a maximum time, these attacks also include keys that have a shorter average computation time.

>>>>

These attacks are ascending in complexity. The timeframe for computing a near-collision was decided as one week with attack strengths of 7 GPU-days \textit{(1 x GPU)}, 70 GPU-days \textit{(10 x GPUs)} and 700 GPU-days \textit{(100 x GPUs)} on a mid-range GPU (AMD RX 480). Due to the long lifetime of PGP keys, 7 days was chosen as a reasonable length of the attack. The tool requires no user interaction once started, therefore, it can be left for an extended period to compute potential keys. This timeframe is also a maximum time, these attacks also include keys that have a shorter average computation time.

### 2019-08-30 Writeup/Thesis/chapters/evaluation.tex
Changes; - TTS run over the entire paper and corrections added

\chapter{Conclusions}
This chapter collates the findings of the paper, evaluates the paper's success against the research questions and discuss potential further work.

@@

The top three metrics (in descending order) were: Levenshtein, NYSIIS and Metaphone. We found that Levenshtein was the most aligned with how people rate phonetically similarity. Levenshtein had a considerable proportion of 4 and 5 ratings (64\%) compared to the alternatives. Levenshtein was also the best performer in the attack context with it having the best attack success rate in all attacks. This corroborates work showing that words with similar spelling tend to share phonetic similarity \cite{hettiarachchi2012sparcl}.
Alongside this, we found Soundex was the least aligned with the human model of similarity with an average rating of just 2 out of 5. This corroborates findings that highlighted major issues with the accuracy of Soundex’s phonetic representation (See Section \ref{sec:soundex}).

@@

\section{Research Question \ref{goal:complexity}}
Research Question \ref{goal:complexity}: \textit{``What are the time and computation complexity required to generate a ’similar’ keys for a targeted key pair?''} has been discussed by the project, the actual generation of keys as shown in Section \ref{sec:key_gen}. Furthermore, the distribution of key permutations on a set of real-world keys were discussed in Section \ref{sec:averagePerms} and \ref{sec:vulnKeys}. To achieve this, the tool GreenOnion was developed. Inspiration for GreenOnion was gathered from a currently available tool known as Scallion. Experimentation results were gathered and displayed in Section \ref{sec:SvG} that showed the significant increase in the number of near-collision keys GreenOnion can test for with GreenOnion being able to handle in excess of 1.5 million keys. This capability is in comparison to the maximum of 2513 keys Scallion can compare. We believe this is due to the implementation of the bloom filter. Its unique characteristics of $O(k)$ complexity regardless of number of elements in the structure allows a huge number of concurrent checks to occur.

\section{Research Question \ref{goal:attackPercentage}}
Research Question \ref{goal:attackPercentage} \textit{``What percentage of attacks successfully deceive a user?''} was shown by the results presented in Section \ref{sec:exp2}. The weakest attack strength and ones that can be computed by a single mid-range GPU for a single week achieved success rate ranging from 9.35\% - 11.01\%. The middle attack involving the use of 10 mid-range GPUs for a week had success rates of 15.20\% - 19.20\%. Finally, the highest attack strength that theoretically involved the use of 100 mid-range GPUs computing for a week has success rates: 24.43\% - 32.05\%. Therefore, showing the number of attacks would deceive a set of users.

@@

\subsection*{Trustword improvements}
The first area of proposed work could be recommendations into how to improve Trustwords backed by empirical evidence. We feel the most promising avenue would be the utilization of Phonetic Vectors unique qualities to identify words of low quality by measuring very low vector distances. For example, present in the dictionary are the words \verb|THERE| and \verb|THEIR|, these could be massively improved upon and could result in a better quality word list. Moreover, utilizing the quantification of dissimilarity could be used to create a dictionary of maximized phonetic distance. This phonetically distinct wordlist could then be assessed in a similar with its success rate quantified against users.

\subsection*{Similar metrics performance}
Another area of further work is the comprehensive assessment of algorithms used to assess phonetic similarity. The algorithms assessed in this work are a very small proportion of potential options. Thus, further work could assess the performance of metrics against each other to determine the one that works best with human models of phonetics. A conclusion could be reached by running the improved experiment discussed in Section \ref{exp:metric}, where it could be repeated with an increased of metrics. Other elements for consideration could be age, location and dialect as variables that affect the metrics performance.

\subsection*{GreenOnion optimizations}
A minimal amount of work and time was allocated to improving the performance of GreenOnion as low-level optimizations are very time-consuming. A project, therefore, could aim to improve on the performance already recorded in this paper. This project could, therefore, improve the performance of the attack and allow for more effective keys to be computed in less time.

>>>>

\chapter{Conclusions}
This chapter collates the findings of the paper, evaluates the paper's success against the research questions and discusses potential further work.

@@

The top three metrics (in descending order) were: Levenshtein, NYSIIS and Metaphone. We found that Levenshtein was the most aligned with how people rate phonetical similarity. Levenshtein had a considerable proportion of 4 and 5 ratings (64\%) compared to the alternatives. Levenshtein was also the best performer in the attack context with it having the highest success rate. This corroborates work showing that words with similar spelling tend to share phonetic similarity \cite{hettiarachchi2012sparcl}.
Alongside this, we found Soundex was the least aligned with the human model of similarity with an average rating of just 2 out of 5. This also corroborates findings that highlighted major issues with the accuracy of Soundex’s phonetic representation (See Section \ref{sec:soundex}).

@@

\section{Research Question \ref{goal:complexity}}
Research Question \ref{goal:complexity}: \textit{``What is the time and computation complexity required to generate a ’similar’ keys for a targeted key pair?''} has been discussed by the project alongside the actual generation of keys as shown in Section \ref{sec:key_gen}. Furthermore, the distribution of key permutations on a set of real-world keys were discussed in Section \ref{sec:averagePerms} and \ref{sec:vulnKeys}. To achieve this, the tool GreenOnion was developed. Inspiration for GreenOnion was gathered from a currently available tool known as Scallion. Experimentation results were gathered and displayed in Section \ref{sec:SvG} that showed the significant increase in the number of near-collision keys GreenOnion can concurrently search for. GreenOnion is able to handle in excess of 1.5 million keys. This capability is in comparison to the maximum of 2513 keys the alternative, Scallion can compare. We believe this is due to the implementation of the bloom filter. Its unique characteristics of $O(k)$ complexity regardless of number of elements in the structure allows a huge number of concurrent checks to occur.

\section{Research Question \ref{goal:attackPercentage}}
Research Question \ref{goal:attackPercentage} \textit{``What percentage of attacks successfully deceive a user?''} was shown by the results presented in Section \ref{sec:exp2}. The weakest attack strength and ones that can be computed by a single mid-range GPU for a single week achieved success rate ranging from 9.35\% - 11.01\%. The middle attack involving the use of 10 mid-range GPUs for a week had success rates of 15.20\% - 19.20\%. Finally, the highest attack strength that theoretically involved the use of 100 mid-range GPUs computing for a week has success rates: 24.43\% - 32.05\%. Therefore, showing the number of attacks required to deceive a set of users.

@@

\subsection*{Trustword improvements}
The first area of proposed work could be recommendations into how to improve Trustwords backed by empirical evidence. We feel the most promising avenue would be the utilisation of Phonetic Vectors unique qualities to identify words of low quality by measuring very low vector distances. For example, present in the dictionary are the words \verb|THERE| and \verb|THEIR|, these could be massively improved upon and could result in a better quality word list. Moreover, utilizing the quantification of dissimilarity could be used to create a dictionary of maximized phonetic distance. This phonetically distinct wordlist could then be assessed in a similar way with its success rate quantified against users.

\subsection*{Similar metrics performance}
Another area of further work is the comprehensive assessment of algorithms used to assess phonetic similarity. The algorithms assessed in this work are a very small proportion of potential options. Thus, further work could assess the performance of metrics against each other to determine the one that works best with human models. A conclusion could be reached by running the improved experiment discussed in Section \ref{exp:metric}, where it could be repeated with an increased number of metrics. Other elements for consideration could be age, location and dialect as variables that affect a metrics performance.

\subsection*{GreenOnion optimizations}
A minimal amount of work was allocated to improving the performance of GreenOnion as low-level optimizations are very time-consuming. A project, therefore, could aim to improve on the performance already recorded in this paper. This project could improve the performance of the attack and allow for more effective keys to be computed in less time.

### 2019-08-30 Writeup/Thesis/chapters/experiments.tex
Changes; - TTS run over the entire paper and corrections added

Even with the discussed issues, the experiment was designed to reduce the number of metrics promptly. This experiment, therefore, has achieved that goal of providing three metrics for the subsequent experiment while balancing between accuracy and expenditure. The results are also an improvement over informal ad-hoc methods. Further work could aim to reproduce this study with the proposed audio-based design (See Section \ref{sec:exp1_considerations}).

@@

The reduced set of 369 participants had an average age of 36.63 ($\sigma = 11.35$) and consisted of an almost equal split of Male (50.4\%) to Female (49.6\%). Around 62\% of participants had completed a single stage of university (Bachelor and up). This aspect makes this set of participants more educated than the general population. All participants were also sourced from the USA and have rated themselves as fully native English speakers.
\begin{table}[!h]
    \centering
    \begin{tabular}{|l|l|}
        \hline
        Browser & Percentage \\
        \hline
        Chrome & 85.1\% \\
        Firefox & 12.2\% \\
        Safari & ~~1.9\% \\
        Other & ~~0.8\% \\
        \hline
    \end{tabular}
    \caption{Internet Browser breakdown}
    \label{tab:exp2_browser}
    \begin{tabular}{|l|l|}
        \hline
        Operating System & Percentage \\
        \hline

@@

\subsection*{Results}
Table \ref{tab:exp2_attacks} contains the break down of results for the experiment. It can be seen that the best metric out of the set was Levenshtein with an overall success of 19.80\%. The best performer, when regarding attack strength, as expected, is the \XOOX~attack. Levenshtein's \XOOX~attack performed the best overall with a success rate of 32.05\%. The worst performer was Metaphone, with an average of 16.88\% over its three levels of attacks. When comparing the performance of the metrics to the previous experiment the ordering remains the same with Levenshtein, NYSIIS and Metaphone all ranking in the same order.

@@

Other relevant work by \textbf{S. Dechand \textit{el al.}}\cite{dechand2016empirical} also discussed in Chapter \ref{cha:LiteratureReview} assess the success rate of attacks on words. Their experiment is less similar as 14 words per attack were assessed with each participant, where the comparison was performed visually. However, the success was 8.78\%. As 10/14 words were kept static, this result is more comparable to the highest attack strength ``2 static''. This, therefore, leads to another 3 fold improvement in the success rates of our simulated attacks.

@@

\begin{table}[!h]
    \makebox[\textwidth][c]{
        \centering
        \begin{tabular}{|llll|}
            \hline
            \textbf{Metric} & & \textbf{Mean matches} & \textbf{Compute Time} \\
            \hline
            NYSIIS &&& \\
            \hline
            & \OOOO & 1963.07 &  ~~27.19 days \\
            & \XOOO & 448.37 &  119.14 days \\
            & \XOOX & 98.07 &  ~~~~1.49 years \\
            \hline\hline

@@

\section{Distribution of vulnerable keys}
\label{sec:vulnKeys}
As discussed in the design of the second experiment (See Section \ref{sec:exp2}), the attacks sampled from a list of `vulnerable keys'. These vulnerable keys were created using real keys extracted from PGP key servers. These keys were then randomly sampled and used to create the combined key,as discussed in Section \ref{sec:pep}. 100,000 random key pairs were created and used as the sample\cite{davidnorman_2019}. Any vulnerable keys in this set were recorded and used in the experiment.

@@

\section{Generation of keys}
\label{sec:key_gen}
In order to demonstrate that the generation of the near-collision keys is not only theoretical, the actual generation was performed using GreenOnion. A random metric was selected from the three carried forward from the first experiment. Alongside this, a random uncontrolled key was generated as the simulated attack target (See Appendix \ref{appendix:uncontrolled_key} for the armor public key). Then for each attack level (\OOOO, \XOOO, \XOOX), a key was computed. NYSIIS was chosen as the selected metric. To expedite the process, an initial search was performed for controlled keys that had the highest number of near-collisions; this was due to the demonstrative purpose of this experiment. Producing near-matching keys from key pairs with a very small number of potential matches adds very little to this demonstration. This, however, will result in best-case scenario key computation times.

@@

As can be seen most notably from Table \ref{tab:nysiis2}, the generation of the actual Trustwords differs in only 3 characters making it arguably very similar. When linking this generated key to results of the second experiment (See Section \ref{sec:exp2}) computation of 2.53 days on a single mid-range GPU can achieve around a 28\% success rate when assessed against actual users. Even with the least restricted attack type presented in Table \ref{tab:nysiis0}, the computation of half a day can provide almost a 10\% success rate when attacking users. This results in any user with a single commodity GPU could compute enough keys in less than a week to have a very high probability of deceiving an actual user.

>>>>

Even with the discussed issues, the experiment was designed to reduce the number of metrics promptly. This experiment, therefore, has achieved that goal of providing three metrics for the subsequent experiment while balancing between accuracy and expenditure. The results are also an improvement over informal ad-hoc methods. Further work could aim to reproduce this study with the proposed audio-based design.

@@

The reduced set of 369 participants had an average age of 36.6 ($\sigma = 11.35$) and consisted of an almost equal split of Male (50.4\%) to Female (49.6\%). Around 62\% of participants had completed a single stage of university (Bachelor and up). This aspect makes this set of participants more educated than the general population. All participants were also sourced from the USA and have rated themselves as fully native English speakers.
\begin{table}[!h]
    \centering
    \begin{tabular}{|l|l|}
        \hline
        Browser & Percentage \\
        \hline
        Chrome & 85.1\% \\
        Firefox & 12.2\% \\
        Safari & ~~1.9\% \\
        Other & ~~0.8\% \\
        \hline
    \end{tabular}
    \caption{Internet Browser breakdown}
    \label{tab:exp2_browser}
    \begin{tabular}{|l|l|}
        \hline
        Operating System & Percentage \\
        \hline

@@

\subsection*{Results}
Table \ref{tab:exp2_attacks} contains the break down of results for the experiment. It can be seen that the best metric out of the set was Levenshtein with an overall success of 19.8\%. The best performer, when regarding attack strength, as expected, is the \XOOX~attack. Levenshtein's \XOOX~attack performed the best overall with a success rate of 32.1\%. The worst performer was Metaphone, with an average of 16.9\% over its three levels of attacks. When comparing the performance of the metrics to the previous experiment the ordering remains the same with Levenshtein, NYSIIS and Metaphone all ranking in the same order.

@@

Other relevant work by \textbf{S. Dechand \textit{el al.}}\cite{dechand2016empirical} also discussed in Chapter \ref{cha:LiteratureReview} assess the success rate of attacks on words. Their experiment is less similar as 14 words per attack were assessed with each participant, where the comparison was performed visually. However, the success was 8.78\%. As 10/14 words were kept static, this result is more comparable to the highest attack strength (\XOOX). This, therefore, leads to another 3 fold improvement in the success rates of our simulated attacks.

@@

\begin{table}[!h]
    \makebox[\textwidth][c]{
        \centering
        \begin{tabular}{|llll|}
            \hline
            \textbf{Metric} & & \textbf{Near-collision keys} & \textbf{Compute Time} \\
            \hline
            NYSIIS &&& \\
            \hline
            & \OOOO & 1963.07 &  ~~27.19 days \\
            & \XOOO & 448.37 &  119.14 days \\
            & \XOOX & 98.07 &  ~~~~1.49 years \\
            \hline\hline

@@

\section{Distribution of vulnerable keys}
\label{sec:vulnKeys}
As discussed in the design of the second experiment (See Section \ref{sec:exp2}), the attacks sampled from a list of `vulnerable keys'. These vulnerable keys were created using real keys extracted from PGP key servers. These keys were then randomly sampled and used to create the combined key, as discussed in Section \ref{sec:pep}. 100,000 random key pairs were created and used as the sample\cite{davidnorman_2019}. Any vulnerable keys in this set were recorded and used in the experiment.

@@

\section{Generation of keys}
\label{sec:key_gen}
In order to demonstrate that the generation of the near-collision keys is not only theoretical, the actual generation was performed using GreenOnion. A random metric was selected from the three carried forward from the first experiment. Alongside this, a random uncontrolled key was generated as the simulated attack target (See Appendix \ref{appendix:uncontrolled_key} for the armor public key). Then for each attack level (\OOOO, \XOOO, \XOOX), a key was computed. NYSIIS was chosen as the selected metric. To expedite the process, an initial search was performed for controlled keys that had the highest number of near-collisions; this was due to the demonstrative purpose of this experiment. Producing near-matching keys from key pairs with a very small number of potential matches adds very little to this demonstration. This, however, will result in a best-case scenario for key computation times.

@@

As can be seen most notably from Table \ref{tab:nysiis2}, the generation of the actual Trustwords differs in only 3 characters making it arguably very similar. When linking this generated key to results of the second experiment (See Section \ref{sec:exp2}) computation of 2.53 days on a single mid-range GPU can achieve around a 28\% success rate when assessed against actual users. This time, however, has been improved due to the random search for a controlled key with a more favourable number of near-collision keys. Even with the least restricted attack type presented in Table \ref{tab:nysiis0}, the computation of half a day can provide almost a 10\% success rate when attacking users. This results in any user with a single commodity GPU could compute enough keys in less than a week to have a very high probability of deceiving an actual user.
